```{r}
# data wrangling : first dataset
library(tidyverse)
library(readr)
library(leaflet)
library(viridis)
library(sf)
library(countrycode)
library(stringr)
library(plotly)

# import first data set
soccer_data1 <- read_delim("data/transfermarkt_fbref_201718.csv", delim = ";", 
                           escape_double = FALSE, trim_ws = TRUE, show_col_types = FALSE)

# wrangle data
soccer_data2 <- soccer_data1 |>
  select(player, nationality, league) |>
    mutate(
    nationality = str_extract(nationality, "[a-z]{2}"),
    full_country_name = countrycode(nationality, "iso2c", "country.name", warn = TRUE))

# Create a mapping of unmatched values to placeholders
placeholder_mapping <- c(
  "en" = "England",
  "wa" = "Wales",
  "xk" = "Kosovo"
)

# Replace unmatched values based on the mapping
soccer_data2$full_country_name <- ifelse(
  is.na(soccer_data2$full_country_name),
  placeholder_mapping[soccer_data2$nationality],
  soccer_data2$full_country_name
)

#Filter the leagues
Premier_League <- soccer_data2 |>
  filter(league == "Premier League")

La_liga <- soccer_data2 |>
  filter(league == "La Liga")

Bundesliga <- soccer_data2 |>
  filter(league == "Bundesliga")

#Number of players from each country for every league
 Num_players_PremierLeague <- Premier_League |>
  group_by(full_country_name) |>
  summarise(num_players = n())
 
 Num_players_Laliga <- La_liga |>
  group_by(full_country_name) |>
  summarise(num_players = n())
 
 Num_players_Bundesliga <- Bundesliga |>
  group_by(full_country_name) |>
  summarise(num_players = n())
  

# save new data file
write.csv(soccer_data2, "wrangled_dataset.csv", row.names = FALSE)
```


```{r}
#PREMIER LEAGUE

#Create map object
 world_map1 <-  maps::map("world", plot = FALSE, fill = TRUE) |>
    st_as_sf()

# join the world map with the num_players

 PremierLeague_map <- Num_players_PremierLeague |>
   right_join(world_map1, by = c("full_country_name"="ID"))
 
head(PremierLeague_map)

#Create a visualization

map_1 <- ggplot(PremierLeague_map, aes(geometry=geom, fill = num_players)) +
   geom_sf() +
   theme_void() +
   labs(fill = "Number of players"
       , title = "Premier League Map") +
   scale_fill_viridis(option = "magma", direction = -1) +
    coord_sf(lims_method = "geometry_bbox", default_crs = NULL)
ggplotly(map_1)

```
Comments: From this map, we can observe that many players in this league originally come from England. This can be explained by the fact that Premier league is an English league, so many players are English.

```{r}
#LA LIGA

#Create map object
 world_map2 <-  maps::map("world", plot = FALSE, fill = TRUE) |>
    st_as_sf()

# join the world map with the num_players
 La_liga_map <- Num_players_Laliga |>
   right_join(world_map2, by = c("full_country_name"="ID"))
 
head(La_liga_map)

#Create a visualization

map_2 <- ggplot(La_liga_map, aes(geometry=geom, fill = num_players)) +
   geom_sf() +
   theme_void() +
   labs(fill = "Number of players"
       , title = "La liga Map") +
   scale_fill_viridis(option = "magma", direction = -1) +
    coord_sf(lims_method = "geometry_bbox", default_crs = NULL)
ggplotly(map_2)
```
Comments: From this map, we can observe that many players in this league originally come from Spain. This is because La Liga is a Spanish league. 

```{r}
#BUNDESLIGA

#Create map object
 world_map3 <-  maps::map("world", plot = FALSE, fill = TRUE) |>
    st_as_sf()

# join the world map with the num_players
 Bundesliga_map <- Num_players_Bundesliga |>
   right_join(world_map3, by = c("full_country_name"="ID"))
 
head(Bundesliga_map)

#Create a visualization

map_3 <- ggplot(Bundesliga_map, aes(geometry=geom, fill = num_players)) +
   geom_sf() +
   theme_void() +
   labs(fill = "Number of players"
       , title = "Bundesliga Map") +
   scale_fill_viridis(option = "magma", direction = -1) +
    coord_sf(lims_method = "geometry_bbox", default_crs = NULL)
ggplotly(map_3)
```
Comments: From this map, we can observe that many players in this league originally come from Germany. This is because Bundesliga league is a german league.

On all the three maps, you can hover over any area on the map, zoom in and out to better visualize the countries, and as you hover you can see the number of players that come from each country.

